Crossing Origins by Crossing Formats

### 2012-11-30 main.tex
a few global edits

In this section we give concrete examples of the attacks described in 
Section~\ref{sec:cross}, using the PDF format as the running example. We begin
by detailing how the design decision made in the PDF-standard make it 
highly suitable
for creating malicious polyglots.

@@

\subsection{Embedded PDF documents}
\todo{Not sure how well it fits here}
When a PDF document is embedded in a web page, the corresponding plugin 
is executed to render the content. Recall from Section~\ref{sec:cross-origin} 
that the plug-in is selected based 
on the MIME-type, either supplied by the server or in the type attribute, and 
that the browser rely on the plug-in to handle the situation when the MIME-type 
supplied by the server is in appropriate for the plug-in.
In the case of the Adobe Reader plug-in, it disregards the MIME-type
supplied by the server and will attempt to interpret any content as PDF.

@@

Billy's and Jonas' anonimized demos?

>>>>

In this section we give concrete examples of the attacks described in 
Section~\ref{sec:cross}, using the PDF format as the running example. We begin
by detailing how the design decision made in the PDF-standard make it highly suitable
for creating malicious polyglots. Throughout this section Adobe Reader is the 
assumed target. A comparison between readers can be found in Section~\ref{sec:eval}.

@@

%\subsection{Embedded PDF documents}
%\todo{Not sure how well it fits here}
When a PDF document is embedded in a web page, the corresponding plugin 
is executed to render the content. Recall from Section~\ref{sec:cross-origin} 
that the plug-in is selected based 
on the MIME-type, either supplied by the server or in the type attribute, and 
that the browser rely on the plug-in to handle the situation when the MIME-type 
supplied by the server is in appropriate for the plug-in.
In the case of the Adobe Reader plug-in, it disregards the MIME-type
supplied by the server and will attempt to interpret any content as PDF.

@@

Billy's and Jonas' anonymized demos?
